\documentclass[14pt]{article}
\usepackage{amsmath}
\usepackage{listings} % For writing code see http://ctan.org/pkg/listings
\usepackage{graphicx}
\usepackage{float}
\usepackage[margin=1.0in]{geometry}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{natbib}

\bibliographystyle{humannat}

\pagestyle{fancy}

\title{Characterizing terms with noise}
\author{Nico Garavito-Camargo}


\date{}
\begin{document}
\maketitle

\section*{}

\subsection{Noise source in N-body simulations}

\begin{enumerate}
  \item Noise in the expansion itself.
  \item Random distribution of particles in the IC's of the particles. Solution:
    Bootstrap the computation of the coefficients and it's variance.
\end{enumerate}

\subsection{Characterizing noise:}

The noise in the BFE due to the discrete nature of the system was quantify in
Weinberg 1996. Here we briefly summarize the method.
The signal to noise of each coefficient is $S/N=\hat{a}/\sqrt{var({\hat{a}})}$

\begin{equation}\label{eq:var}
  var(\hat{a}_{n,l,m}) = m \left[ \sum_{i}^{N}m_i \Psi_{n,l,m}^2(x_i)
   - \left(\sum_{i}^{N}m_i \Psi_{n,l,m}(x_i)\right)^2
   \right]
\end{equation}

The first term in the right-hand side is the covariance matrix and
the second term of Eq.\ref{eq:var} are the coefficients
$\hat{S}_{n,l,m}^2$ and $\hat{T}_{n,l,m}^2$. $m$ is the particle
mass and $\Psi_{nlm}$ is defined as:

\begin{equation}
  \Psi_{nlm}(x_i) = (2-\delta_{m,0})
  \tilde{A}_{n,l}\Phi_{n,l}(r_i)Y_{l,m}(\theta_i)cos(m\phi_i)
\end{equation}

The covariance matrix is computed as::

\begin{equation}
  \tilde{a}_{nlm n'l'm'} = \hat{a}_{nlm} \hat{a}_{n'l'm'}
\end{equation}

The smoothening of the coefficients is computed as follows:

\begin{equation}
  b_{nlm}(\hat{a}_{nlm}) = \dfrac{1}{1 +
  \frac{var(\hat{a}_{nlm})}{{\hat{a}_{nlm}}^2}}
\end{equation}

In order to characterize the noise due to the random distribution of particles
that are sampling the potential and density.



what a am I using then computing var(a) the one form the sample or the mean?

\subsubsection{The BFE for the MW and the LMC:}

Computed and tested with \verb+Gala+ and a parallel  C code written by me. 


What is the different in the number of terms when doing the bootstrap and when
not?

Any difference in the amplitudes of those terms??


\bibliography{references}



\end{document}
